---
title: "Developing Data Products - Week 3"
author: "Sri"
date: "February 20, 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(plotly)
```

## Instructions

Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. We would love to see you show off your creativity!

## Review Criteria

The rubric contains the following two questions:

1. Does the web page feature a date and is this date less than two months before the date that you're grading this assignment?

2. Is the web page a presentation and does it feature an interactive plot that appears to have been created with Plotly?

## plot_ly & mtcars - Basic 3D scatter plot

```{r mtcars, echo = FALSE, message=FALSE}
set.seed(100)
plot_ly(mtcars, x = ~wt, y = ~hp, z = ~qsec, 
    marker = list(color = ~mpg, colorscale = c('#FF0000', '#00FF00'), showscale = TRUE)) %>%
  add_markers()
```
